---
title: "Stock Market Analysis"
author: "Joshua Omondi"
date: "2/18/2022"
output: html_document
---
## This is a practice project. Getting to learn about RMarkdown. Inspiration is from Ghetto Counselor(https://rpubs.com/markloessi).

```{r setup, include=FALSE}
library(quantmod)
```


```{r cars}
symbolBasket <- c('AAPL', 'AMZN', 'NFLX', 'SPY')
getSymbols(symbolBasket , src='yahoo')
```

## Obtaining summary for Netflix (NFLX)


```{r pressure, echo=FALSE}
summary(`NFLX`)
```
## Data Preparation
```{r}
NFLX <- as.xts(`NFLX`)
names(NFLX)
```

```{r}
names(NFLX) <- c("NFLX.Open"   ,  "NFLX.High"   ,  "NFLX.Low"   ,   "NFLX.Close"  ,  "NFLX.Volume",  "NFLX.Adjusted")
names(NFLX)
```
## Plotting Charts

```{r}
plot(NFLX$NFLX.Open)
```

## Using barchart to plot
```{r}
barChart(NFLX, bar.type = 'hlc', TA = NULL)
```

## Candle Sticks Plot
```{r}
candleChart(NFLX, TA=NULL, subset = '2021')
```

## Stock prices started dropping towards the end of the year. This might be a response to people starting to go back to offices. NFLX is considered a stay-at-home stock.

```{r}
candleChart(NFLX, TA=c(addMACD(),addVo()), subset = '2021')
```
## The above chart shows the moving average convergence divergence (MACD).

```{r}
candleChart(NFLX , TA=c(addMACD()), subset = '2021-11::2022-02', theme = 'white')
```
## The stock has been on a decline, dropping closely to 50% since November 2021.

```{r}
chartSeries(NFLX, 
            type = c("auto", "candlesticks"), 
            subset = '2021-01::',
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            TA=c(addMACD(),addVo()))
```

```{r}
chartSeries(NFLX, 
            type = c("auto", "candlesticks"), 
            subset = '2020-01::',
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = TRUE,
            TA=c(addMACD(),addVo()))
```

```{r}
chartSeries(NFLX, 
            type = c("auto", "candlesticks"), 
            subset = '2021-09::',
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = TRUE,
            TA=c(addMACD(),addVo()))
```

```{r}
chartSeries(NFLX, 
            type = c("auto", "matchsticks"), 
            subset = '2020-01::',
            show.grid = TRUE,
            major.ticks='auto', minor.ticks=TRUE,
            multi.col = FALSE,
            TA=c(addMACD(),addVo(),addSMA(n=200,col = 'blue'),addSMA(n=50,col = 'red'),addSMA(n=22,col = 'green'),
            addROC(n=200,col = 'blue'),addROC(n=50,col = 'red'),addROC(n=22,col = 'green'))) # rate of change
```

